### 2025-03-27 ms/response_letter.tex

Based on the comments, we have updated the manuscript to reflect the
following:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Improved content and clarity:} We clarified the study's main
  objective, added missing methodological details (e.g., wood density
  classification criteria and interpretation of \(\Delta\)LOOIC), and
  expanded the discussion to address potential confounding effects on
  allometric relationships.
\item
  \textbf{Enhanced presentation and formatting:} We standardized the
  reporting of parameters, corrected figure labels, restructured
  supplementary tables for better readability, and revised the
  manuscript language to improve clarity and consistency.
\end{enumerate}

We believe these revisions have strengthened the manuscript by
clarifying our objectives, improving consistency and readability, and
addressing key methodological concerns---thereby better highlighting the
significance of our findings.

We have also updated the data availability statement. The programming
code of this study will be deposited at Zenodo (https://zenodo.org) and
made available on Github
(\url{https://github.com/duyenecology/tree-allo}).

@@

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  Supplementary Table S6 is very congested and hard to read. Please
  revise for better understanding.
\end{enumerate}
\end{quote}

We have reformatted Supplementary Tables S6, S7, and S8 for improved
readability and included detailed captions to aid interpretation.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{8}
\tightlist
\item
  A revision of the English is needed as some sentences aren't properly
  structured, and it's often difficult to grasp what the authors are
  saying.
\end{enumerate}
\end{quote}

We have revised the manuscript for language, grammar, and sentence
structure to enhance clarity and improve overall readability. For
example, we revised lines XXX--YYY in the Discussion section to ensure
sentence brevity and clarity. Additionally, we updated the figure
legends and table captions for greater clarity and carefully
cross-checked all technical terms to maintain consistency throughout the
text.

### 2025-03-27 ms/ms.qmd

Our analysis combined tree allometry data from Tallo, which includes standardized measurements of DBH, height, and crown radius for 5,163 species across various biomes [@Jucker2022, https://doi.org/10.5281/zenodo.6637599] along with wood density data for 10,995 species from TRY version 6 [@Kattge2020, https://www.try-db.org/TryWeb/Home.php] (see Supplementary Table S1 for further details).
We thoroughly processed the Tallo dataset by removing 998 outliers following @Jucker2022.
To ensure consistency, we selected only species with standardized wood density values in g cm^-3^ from TRY and removed any records with missing data.
Subsequently, we created an overlapping dataset between Tallo and TRY, resulting in a combined dataset encompassing allometric and wood density information for `r data_params$ori_sample_size` individuals across `r data_params$ori_species_number` species.

@@

Statistical analyses were performed in R version 4.3.2 [@RCoreTeam2023], using the R packages *targets* version 1.7.0 for workflow management [@Landau2021].
Codes are made available on GitHub at <https://github.com/duyenecology/tree-allometry> (Stan code is provided in Supplementary Section S2).

@@

\newpage
# Acknowledgments {.unnumbered}

@@

Tallo and TRY data are available from their respective platforms.
Codes are available from Zenodo at xxx

>>>>

Our analysis combined tree allometry data from Tallo, which includes standardized measurements of DBH, height, and crown radius for 5,163 species across various biomes [@Jucker2022], with wood density data for 10,995 species from TRY version 6 [@Kattge2020] (see Supplementary Table S1 for further details).
Detailed information on data access and availability can be found in the Data availability section.
We thoroughly processed the Tallo dataset by removing 998 outliers following @Jucker2022.
To ensure consistency, we selected only species with standardized wood density values in g cm^-3^ from TRY and removed any records with missing data.
Subsequently, we created an overlapping dataset between Tallo and TRY, resulting in a combined dataset encompassing allometric and wood density information for `r data_params$ori_sample_size` individuals across `r data_params$ori_species_number` species.

@@

Statistical analyses were performed in R version 4.3.2 [@RCoreTeam2023], using the R packages *targets* version 1.7.0 for workflow management [@Landau2021].
Codes are made available on Zenodo (https://zenodo.org) and GitHub (<https://github.com/duyenecology/tree-allo>).
Stan code is provided in Supplementary Section S2.

@@

# Acknowledgments {.unnumbered}

@@

The tree allometry data is avaiable from tallo [@Jucker2022, https://doi.org/10.5281/zenodo.6637599], and
the wood density data are available on request from TRY version 6  [@Kattge2020, <https://www.try-db.org/TryWeb/Home.php>].
All codes and scripts used for analysis are available on Zenodo (https://zenodo.org) and GitHub (<https://github.com/duyenecology/tree-allo>).

### 2025-03-27 ms/ms.tex

Our analysis combined tree allometry data from Tallo, which includes
standardized measurements of DBH, height, and crown radius for 5,163
species across various biomes (\citeproc{ref-Jucker2022}{Jucker et al.
2022}, https://doi.org/10.5281/zenodo.6637599) along with wood density
data for 10,995 species from TRY version 6
(\citeproc{ref-Kattge2020}{Kattge et al. 2020},
https://www.try-db.org/TryWeb/Home.php) (see Supplementary Table S1 for
further details). We thoroughly processed the Tallo dataset by removing
998 outliers following Jucker et al. (\citeproc{ref-Jucker2022}{2022}).
To ensure consistency, we selected only species with standardized wood
density values in g cm\textsuperscript{-3} from TRY and removed any
records with missing data. Subsequently, we created an overlapping
dataset between Tallo and TRY, resulting in a combined dataset
encompassing allometric and wood density information for 355,881
individuals across 2,961 species.

@@

Statistical analyses were performed in R version 4.3.2
(\citeproc{ref-RCoreTeam2023}{R Core Team 2023}), using the R packages
\emph{targets} version 1.7.0 for workflow management
(\citeproc{ref-Landau2021}{Landau 2021}). Codes are made available on
GitHub at \url{https://github.com/duyenecology/tree-allometry} (Stan
code is provided in Supplementary Section S2).

@@

Tallo and TRY data are available from their respective platforms. Codes
are available from Zenodo at xxx

>>>>

Our analysis combined tree allometry data from Tallo, which includes
standardized measurements of DBH, height, and crown radius for 5,163
species across various biomes (\citeproc{ref-Jucker2022}{Jucker et al.
2022}), with wood density data for 10,995 species from TRY version 6
(\citeproc{ref-Kattge2020}{Kattge et al. 2020}) (see Supplementary Table
S1 for further details). Detailed information on data access and
availability can be found in the Data availability section. We
thoroughly processed the Tallo dataset by removing 998 outliers
following Jucker et al. (\citeproc{ref-Jucker2022}{2022}). To ensure
consistency, we selected only species with standardized wood density
values in g cm\textsuperscript{-3} from TRY and removed any records with
missing data. Subsequently, we created an overlapping dataset between
Tallo and TRY, resulting in a combined dataset encompassing allometric
and wood density information for 355,881 individuals across 2,961
species.

@@

Statistical analyses were performed in R version 4.3.2
(\citeproc{ref-RCoreTeam2023}{R Core Team 2023}), using the R packages
\emph{targets} version 1.7.0 for workflow management
(\citeproc{ref-Landau2021}{Landau 2021}). Codes are made available on
Zenodo (https://zenodo.org) and GitHub
(\url{https://github.com/duyenecology/tree-allo}). Stan code is provided
in Supplementary Section S2.

@@

The tree allometry data is avaiable from tallo
(\citeproc{ref-Jucker2022}{Jucker et al. 2022},
https://doi.org/10.5281/zenodo.6637599), and the wood density data are
available on request from TRY version 6
(\citeproc{ref-Kattge2020}{Kattge et al. 2020},
\url{https://www.try-db.org/TryWeb/Home.php}). All codes and scripts
used for analysis are available on Zenodo (https://zenodo.org) and
GitHub (\url{https://github.com/duyenecology/tree-allo}).

### 2025-03-27 sup/sup_old.qmd

---
fontsize: 12pt
geometry: margin=1in
link-citations: true
bibliography: "../ms/tree-allometry.bib"
csl: "../ms/journal-of-forestry-research.csl"
crossref:
  fig-title: Figure
  fig-prefix: Figure
  tbl-title: Table
  eq-prefix: Eq.
format:
  pdf:
    toc: false
    keep-tex: true
    latex-clean: false
    pdf-engine: xelatex
    include-in-header:
      text: |
        \usepackage[default]{sourcesanspro}
        \usepackage{sourcecodepro}
        \usepackage{lineno}
        \usepackage{setspace}
        \renewcommand{\thetable}{S\arabic{table}}
        \renewcommand{\thefigure}{S\arabic{figure}}
    prefer-html: true
  docx:
    toc: false
    include-in-header:
      text: |
        \usepackage[default]{sourcesanspro}
        \usepackage{lineno}
        \linespread{1.2}

@@

**Nguyen and Katabuchi, Saturating allometric relationships reveal how wood density shapes global tree architecture**

@@

**Table S2.** Characteristics of the sub-datasets used to select the best predictive model for each allometric relationship in angiosperms and gymnosperms.

@@

**Table S6.** Parameter estimates for predicting tree height (m) from DBH (cm) of 1290 species (see file *TableS6_height_sp_estimates.xlsx*).

**Table S7.** Parameter estimates for predicting crown radius (m) from DBH (cm) of 821 species (see file *TableS7_crown_radius_sp_estimates.xlsx*).

**Table S8.** Parameter estimates for predicting DBH (cm) from crown radius (m) and tree height (m) of 800 species (see file *TableS8_dbh_sp_estimates.xlsx*).

**Figure S1.** Functional curves describing allometric relationships of tree dimensions with DBH on the log scale.

@@

**Table S2**: Characteristics of the sub-datasets used to select the best predictive model for each allometric relationship in angiosperms and gymnosperms.
The ranges represent the minimum and maximum values for the respective variables: DBH (cm), tree height (H, m), crown radius (CR, m), and wood density (WD, g cm^-3^).

@@

```{r echo=FALSE, results='asis'}
posterior_df <- tar_read(posterior_df)

posterior_df <- posterior_df |>
  mutate(
    Intercept_CI = sapply(Intercept_CI, format_ci),
    Slope_CI = sapply(Slope_CI, format_ci),
    Tau_CI = sapply(Tau_CI, format_ci)
  )

df_h <- posterior_df |>
  filter(Dependent_variable == "Tree Height") |>
  dplyr::select(-Dependent_variable) |>
  mutate(
    Functional_form = factor(Functional_form, levels = c("Power-Law", "gMM", "Weibull")),
    Wood_density = factor(Wood_density, levels = c("Without", "With"))
  ) |>
  arrange(Division, Functional_form, Wood_density)

@@

```{r echo=FALSE, results='asis'}
posterior_df <- tar_read(posterior_df)

posterior_df <- posterior_df |>
  mutate(
    Intercept_CI = sapply(Intercept_CI, format_ci),
    Slope_CI = sapply(Slope_CI, format_ci),
    Tau_CI = sapply(Tau_CI, format_ci)
  )

df_cr <- posterior_df |>
  filter(Dependent_variable == "Crown Radius") |>
  dplyr::select(-Dependent_variable) |>
  mutate(
    Functional_form = factor(Functional_form, levels = c("Power-Law", "gMM", "Weibull")),
    Wood_density = factor(Wood_density, levels = c("Without", "With"))
  ) |>
  arrange(Division, Functional_form, Wood_density)

@@

```{r echo=FALSE, results='asis'}
posterior_df <- tar_read(posterior_df)

posterior_df <- posterior_df |>
  mutate(
    Intercept_CI = sapply(Intercept_CI, format_ci),
    Slope_CI = sapply(Slope_CI, format_ci),
    Tau_CI = sapply(Tau_CI, format_ci)
  )
df_dbh <- posterior_df |>
  filter(Dependent_variable %in% c("DBH", "DBH1", "DBH2", "DBH3")) |>
  mutate(
    Predictor = case_when(
      Dependent_variable == "DBH1" ~ "CR × H",
      Dependent_variable == "DBH2" ~ "CR",
      Dependent_variable == "DBH3" ~ "H",
      Dependent_variable == "DBH" ~ "CR, H",
      TRUE ~ NA_character_
    )
  ) |>
  dplyr::select(-Dependent_variable)

@@

![
Allometric relationships between tree height and crown radius versus DBH for angiosperms (a, c) and gymnosperms (b, d) based on three different models: power-law (orange), generalized Michaelis-Menten (green), and Weibull (blue).
The density of overlapping points is represented using a colour gradient ranging from black (low density) to yellow (high density).
Point density was calculated using a 2D kernel density estimation on a 300 $\times$ 300 grid, which estimate the concentration of data points in the log-transformed DBH and tree height or crown radius.
All axes are shown on the log scale.
](../figs/h_cr_dbh_log.png){#fig-compare fig-pos="H"}

>>>>

---
fontsize: 12pt
geometry: margin=1in
link-citations: true
bibliography: "../ms/tree-allometry.bib"
csl: "../ms/journal-of-forestry-research.csl"
crossref:
  fig-title: Figure
  fig-prefix: Figure
  tbl-title: Table
  eq-prefix: Eq.
format:
  pdf:
    toc: false
    keep-tex: true
    latex-clean: false
    pdf-engine: xelatex
    include-in-header:
      text: |
        \usepackage[default]{sourcesanspro}
        \usepackage{sourcecodepro}
        \usepackage{lineno}
        \usepackage{setspace}
        \doublespacing
        \linenumbers
        \renewcommand{\thetable}{S\arabic{table}}
        \renewcommand{\thefigure}{S\arabic{figure}}
    prefer-html: true
  docx:
    toc: false
    include-in-header:
      text: |
        \usepackage[default]{sourcesanspro}
        \usepackage{lineno}
        \linespread{1.2}

@@

**Saturating allometric relationships reveal how wood density shapes global tree architecture**

@@

**Table S2.** Characteristics of sub-datasets were used to select the best predictive model of each allometric relationship for angiosperms and gymnosperms.

@@

**Table S6.** Parameter estimates for predicting tree height (m) from DBH (cm) of 1290 species (see file TableS6_height_sp_estimates.xlsx).

**Table S7.** Parameter estimates for predicting crown radius (m) from DBH (cm) of 821 species (see file TableS7_crown_radius_sp_estimates.xlsx).

**Table S8.** Parameter estimates for predicting DBH (cm) from crown radius (m) and tree height (m) of 800 species (see file TableS8_dbh_sp_estimates.xlsx).

**Figure S1.** Function curves are used to describe allometric relationships of tree dimensions with DBH in log scale.

@@

**Table S2**: Characteristics of sub-datasets used to select the best predictive model of each allometric relationship for angiosperms and gymnosperms.
The ranges represent the minimum and maximum values for the respective variables: DBH (cm), tree height (H, m), crown radius (CR, m), and wood density (WD, g cm$^{-3}$).

@@

```{r echo=FALSE, results='asis'}
posterior_rounded_df <- tar_read(posterior_rounded_df)
df_h <- posterior_rounded_df |>
  filter(Dependent_variable == "Tree Height") |>
  dplyr::select(-Dependent_variable) |>
  mutate(
    Functional_form = factor(Functional_form, levels = c("Power-Law", "gMM", "Weibull")),
    Wood_density = factor(Wood_density, levels = c("Without", "With"))
  ) |>
  arrange(Division, Functional_form, Wood_density)

@@

```{r echo=FALSE, results='asis'}
posterior_rounded_df <- tar_read(posterior_rounded_df)
df_cr <- posterior_rounded_df |>
  filter(Dependent_variable == "Crown Radius") |>
  dplyr::select(-Dependent_variable) |>
  mutate(
    Functional_form = factor(Functional_form, levels = c("Power-Law", "gMM", "Weibull")),
    Wood_density = factor(Wood_density, levels = c("Without", "With"))
  ) |>
  arrange(Division, Functional_form, Wood_density)

@@

```{r echo=FALSE, results='asis'}
posterior_rounded_df <- tar_read(posterior_rounded_df)

df_dbh <- posterior_rounded_df |>
  filter(Dependent_variable %in% c("DBH", "DBH1", "DBH2", "DBH3")) |>
  mutate(
    Predictor = case_when(
      Dependent_variable == "DBH1" ~ "CR × H",
      Dependent_variable == "DBH2" ~ "CR",
      Dependent_variable == "DBH3" ~ "H",
      Dependent_variable == "DBH" ~ "CR, H",
      TRUE ~ NA_character_
    )
  ) |>
  dplyr::select(-Dependent_variable)

@@

![
Allometric relationships between tree height and crown radius with DBH of angiosperm (a, c) and gymnosperm (b, d) based on three different models: power-law (orange), generalized Michaelis-Menten (green), and Weibull (blue).
The density of overlapping points is shown using a colour gradient ranging from black (low density) to yellow (high density).
Point density was calculated using a 2D kernel density estimation on a 300 $\times$ 300 grid, estimating the concentration of data points in the log-transformed space of DBH and tree height or crown radius.
All axes are on the log scale.
](../figs/h_cr_dbh_log.png){#fig-compare fig-pos="H"}
